Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-06 policies.tex
Spacing around tables/figures.
Edits based on Mohamed's comments.

% Slack
\begin{figure} \begin{center}
\includegraphics[width=\columnwidth]{figs/slack.pdf} \vspace{-0.2in}
\caption{Slack and its effect on monitoring over time.}
\label{fig:policies.slack} \vspace{-0.1in} \end{center} \end{figure}

@@

\begin{figure} 
  \begin{center} 
    \subfloat[Unrestricted Dropping] {
      \includegraphics[width=\columnwidth]{figs/unrestricted_drop.pdf}
      \label{fig:policies.all_drop} 
    }
    \vspace{-0.1in} \\ 
    \subfloat[Source-Only Dropping] { 
      \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
      \label{fig:policies.source_drop} 
    } 
    \vspace{-0.1in} \\ 
    \subfloat[Sub-Flow Dropping] { 
      \includegraphics[width=\columnwidth]{figs/subflow_drop.pdf}
      \label{fig:policies.subflow_drop} 
    } 
  \end{center} 
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.} 
  \label{fig:policies.policies} 
\end{figure}

@@

More complex dropping policies can be implemented given more detailed
information about the monitoring dependence graph. This information can be
found through static analysis or profiling, though we do not explore how to
find it in detail here. Given this information, we describe one possible
policy to use it, which we call \emph{sub-flow dropping}. Sub-flow dropping makes
dropping decisions at a granularity in between unrestricted dropping and
source-only dropping (see Figure~\ref{fig:policies.subflow_drop}). 
The basic idea of sub-flow dropping is to drop portions of the monitoring
dependence graph at the smallest granularity such that no work is wasted.
Sub-flow dropping allows source nodes to be dropped and nodes after branch
points in the monitoring dependence graph to be dropped. From
Figure~\ref{fig:policies.subflow_drop}, this corresponds to nodes {\tt A}, {\tt
C}, and {\tt F}. For example,
dropping node {\tt C} causes nodes {\tt D} and {\tt E} to be skipped. However,
performing monitoring on the remaining nodes allows the check at node {\tt G}
to be performed with no wasted work. Similarly, dropping {\tt F} allows node
{\tt E} to be checked with no wasted work.

%Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
%comparison of where dropping decisions are made for these two policies. 
Source-only dropping will
result in no wasted work and thus better coverage at a given overhead than unrestricted dropping. However, because of the coarser-grained decision, it
may be more difficult to closely match overhead targets. 
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping in terms of matching overhead and coverage achieved.
Sub-flow dropping can still result in wasted work if there are merge points in
the monitoring dependence graph and only one part of the incoming flows is
dropped, but should result in less wasted work than
unrestricted dropping. Thus, its coverage falls in between that of source-only
dropping and unrestricted dropping. Similarly, sub-flow dropping's ability to
closely match overhead targets falls between that of source-only dropping and
unrestricted dropping.
We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since every event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event is likely to cause the final check to be
invalid by dropping at least one event in the chain.

>>>>

% Slack
\begin{figure} 
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/slack.pdf} 
    \vspace{-0.1in}
    \caption{Slack and its effect on monitoring over time.}
    \label{fig:policies.slack} 
    \vspace{-0.3in} 
  \end{center} 
\end{figure}

@@

\begin{figure} 
  \begin{center} 
    \subfloat[Unrestricted Dropping] {
      \includegraphics[width=\columnwidth]{figs/unrestricted_drop.pdf}
      \label{fig:policies.all_drop} 
    }
    \\
    \subfloat[Source-Only Dropping] { 
      \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
      \label{fig:policies.source_drop} 
    } 
    \\
    \subfloat[Sub-Flow Dropping] { 
      \includegraphics[width=\columnwidth]{figs/subflow_drop.pdf}
      \label{fig:policies.subflow_drop} 
    } 
  \end{center} 
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.} 
  \label{fig:policies.policies} 
  \vspace{-0.2in}
\end{figure}

@@

More complex dropping policies can be implemented given more detailed
information about the monitoring dependence graph. This information can be
found through static analysis or profiling, though we do not explore how to
find it in detail here. Given this information, we describe one possible
policy to use it, which we call \emph{sub-flow dropping}. Sub-flow dropping makes
dropping decisions at a granularity in between unrestricted dropping and
source-only dropping (see Figure~\ref{fig:policies.subflow_drop}). 
The basic idea of sub-flow dropping is to drop portions of the monitoring
dependence graph at the smallest granularity such that no work is wasted.
Sub-flow dropping allows source nodes to be dropped and nodes after branch
points in the monitoring dependence graph to be dropped. From
Figure~\ref{fig:policies.subflow_drop}, this corresponds to nodes {\tt A}, {\tt
C}, and {\tt F}. For example,
dropping node {\tt C} causes nodes {\tt D} and {\tt E} to be skipped. However,
performing monitoring on the remaining nodes allows the check at node {\tt G}
to be performed with no wasted work. Similarly, dropping {\tt F} allows node
{\tt E} to be checked with no wasted work.
Note that sub-flow dropping can still result in wasted work if there are merge
points in the monitoring dependence graph and only part of the incoming flows
are dropped, but it should result in less wasted work than compared to an
unrestricted dropping policy.

%Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
%comparison of where dropping decisions are made for these two policies. 
Source-only dropping will
result in no wasted work and thus better coverage at a given overhead than
unrestricted dropping. However, because of the coarser-grained decision, it
may be more difficult to closely match overhead targets. 
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping in terms of matching overhead and coverage achieved.
If the monitoring dependence graph is highly connected, then source-only
dropping will perform poorly. On the other hand, we expect source-only dropping 
to work well when there are a large number of independent metadata flows.
Monitoring dependence graphs with a large number of branches will favor a
sub-flow dropping policy.

The choice of dropping policy can also depend on whether probabilistic dropping
is performed instead of slack-based dropping.
Probabilistic dropping works poorly with an
unrestricted dropping policy. Since every event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event is likely to cause the final check to be
invalid by dropping at least one event in the chain. Instead, source-only
dropping works well when performing probabilistic dropping.
